Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-21 WSSSPE4_report/wg_access.tex
give more details about NeIC work

%Introduction to group here, including the overall objective of work in this area.
Each developer of software with uncommon needs (hardware, software, libraries, data sets) or non-public code must acquire, setup, and maintain their own continuous integration systems because their needs make them ineligible for popular free services such as Travis CI.  For example, software groups that develop BIOUNO, CI4SI, GROMACS) have done this.

@@

%What are the first SMART steps proposed?
\begin{enumerate}
\item Learn how donate machines to Debian
\item Find funding, perhaps via NEIC? (\url{https://wiki.neic.no/wiki/NeIC_Community_Wiki}) 
\item Build community
\end{enumerate}

>>>>

%Introduction to group here, including the overall objective of work in this area.
Each developer of software with uncommon needs (hardware, software, libraries, data sets), non-public code, or tests that exceed time limits for free plans must acquire, setup, and maintain their own continuous integration systems because their needs make them ineligible for popular free services such as Travis CI.  For example, software groups that develop BIOUNO, CI4SI, or GROMACS have done this.

@@

%What are the first SMART steps proposed?
\begin{enumerate}
\item Learn how to donate machines to Debian
\item Find funding, perhaps via NEIC? (\url{https://wiki.neic.no/wiki/NeIC_Community_Wiki}) 
\item Build community
\end{enumerate}
